---
title: "Journal (reproducible report)"
author: "Hendrik Rogoll"
date: "2020-11-05"
output:
  html_document:
    toc: true
    toc_float: true
    collapsed: false
    number_sections: true
    toc_depth: 3
    #code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(message=FALSE,warning=FALSE, cache=TRUE)
```

**IMPORTANT:** You can delete everything in here and start fresh. You might want to start by not deleting anything above this line until you know what that stuff is doing.

This is an `.Rmd` file. It is plain text with special features. Any time you write just like this, it will be compiled to normal text in the website. If you put a \# in front of your text, it will create a top level-header.

# My first post

Last compiled: `r Sys.Date()`

Notice that whatever you define as a top level header, automatically gets put into the table of contents bar on the left. 

## Second level header

You can add more headers by adding more hashtags. These won't be put into the table of contents

### third level header

Here's an even lower level header

# My second post (note the order)

Last compiled: `r Sys.Date()`

I'm writing this tutorial going from the top down. And, this is how it will be printed. So, notice the second post is second in the list. If you want your most recent post to be at the top, then make a new post starting at the top. If you want the oldest first, do, then keep adding to the bottom

# Adding R stuff

So far this is just a blog where you can write in plain text and serve your writing to a webpage. One of the main purposes of this lab journal is to record your progress learning R. The reason I am asking you to use this process is because you can both make a website, and a lab journal, and learn R all in R-studio. This makes everything really convenient and in the same place. 

So, let's say you are learning how to make a histogram in R. For example, maybe you want to sample 100 numbers from a normal distribution with mean = 0, and standard deviation = 1, and then you want to plot a histogram. You can do this right here by using an r code block, like this:

```{r}
samples <- rnorm(100, mean=0, sd=1)
hist(samples)
```

When you knit this R Markdown document, you will see that the histogram is printed to the page, along with the R code. This document can be set up to hide the R code in the webpage, just delete the comment (hashtag) from the cold folding option in the yaml header up top. For purposes of letting yourself see the code, and me see the code, best to keep it the way that it is. You'll learn that all of these things and more can be customized in each R code block.

# Challenge One

```{r plot, fig.width=10, fig.height=7}

# Introduction of challenge one ----

library(tidyverse)
library(readxl)
library(lubridate)

bike_orderlines_wrangled_tbl <- read_excel("DS_101/00_data/01_bike_sales/02_wrangled_data/bike_orderlines.xlsx")

# bike_orderlines_wrangled_tbl
# glimpse(bike_orderlines_wrangled_tbl)

location_bike_orderlines_wrangled_tbl <- bike_orderlines_wrangled_tbl %>%
  separate(col = location,
           into = c("city", "state"),
           sep = ", ") 

# glimpse(location_bike_orderlines_wrangled_tbl)

# 1. Part of challenge one ----

sales_by_state_tbl <- location_bike_orderlines_wrangled_tbl %>%
  select(state, total_price) %>%
  group_by(state) %>%
  summarise(revenue = sum(total_price)) %>%
  mutate(revenue_text = scales::dollar(revenue, big.mark = ".", 
                                       decimal.mark = ",", 
                                       prefix = "", 
                                       suffix = " €"))
# sales_by_state_tbl

sales_by_state_tbl %>%
  ggplot(aes(x = state, y = revenue)) +
  geom_col(fill = "#2DC6D6") +
  geom_label(aes(label = revenue_text)) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  scale_y_continuous(labels = scales::dollar_format(big.mark = ".", 
                                                    decimal.mark = ",", 
                                                    prefix = "", 
                                                    suffix = " €")) +
  labs(
    title    = "Revenue by state",
    subtitle = " ",
    x = "",
    y = "Revenue"
  )

# 2. Part of challenge one ----

sales_by_state_year_tbl <- location_bike_orderlines_wrangled_tbl %>%
  select(state, total_price, order_date) %>%
  mutate(year = year(order_date)) %>%
  group_by(state, year) %>%
  summarise(revenue = sum(total_price)) %>%
  ungroup() %>%
  mutate(revenue_text = scales::dollar(revenue, big.mark = ".", 
                                       decimal.mark = ",", 
                                       prefix = "", 
                                       suffix = " €"))
# sales_by_state_year_tbl

sales_by_state_year_tbl %>%
  ggplot(aes(x = year, y = revenue, fill = state)) +
  geom_col() +
  geom_smooth(method = "lm", se = FALSE) +
  facet_wrap(~ state) +
  scale_y_continuous(labels = scales::dollar_format(big.mark = ".", 
                                                    decimal.mark = ",", 
                                                    prefix = "", 
                                                    suffix = " €")) +
  labs(
    title = "Revenue by year and main category",
    subtitle = " ",
    fill = "State"
  )

```

# Challenge Two

## Part One

``` {r}

library(tidyverse)
library(httr)
library(glue)
library(jsonlite)

# All NBA Teams

# resp <- GET("https://www.balldontlie.io/api/v1/players/<ID>")

nba_api <- function(path) {
  url <- modify_url(url = "https://www.balldontlie.io", path = glue("/api/v1{path}"))
  resp <- GET(url)
  stop_for_status(resp) # automatically throws an error if a request did not succeed
}

resp <- nba_api("/players/1")
resp

teams <- resp %>% 
  .$content %>% 
  rawToChar() %>% 
  fromJSON()

teams

```

## Part Two

For this challenge the website from rosebikes was scraped. As a result all bikes for all categories are shown, which are available with the same code, thus a few categories were ignored. Additionally, all bikes are summed up in one tibble.

``` {r}
# Libraries ----

library(tidyverse) # Main Package - Loads dplyr, purrr, etc.
library(rvest)     # HTML Hacking & Web Scraping
library(xopen)     # Quickly opening URLs
library(jsonlite)  # converts JSON files to R objects
library(glue)      # concatenate strings
library(stringi)   # character string/text processing

# Bike-Category Links ----

url_home <- "https://www.rosebikes.de/fahrr%C3%A4der"
html_home <- read_html(url_home)

bike_category_url_tbl <- html_home %>%
  
  html_nodes(css = ".catalog-navigation__link") %>%
  html_attr('href') %>%
  
  
  # Categories Sale, Kinder, E-Bike and Bike-Finder ignored
  discard(.p = ~stringr::str_detect(.x,"sale|zoovu|kinder|e-bike")) %>%
  
  enframe(name = "position", value = "subdirectory") %>%
  
  mutate(
    url = glue("https://www.rosebikes.de{subdirectory}")
  ) %>%
  
  distinct(url)

# bike_category_url_tbl

bike_category_char_tbl <- html_home %>%
  html_nodes(css = ".catalog-categories-item__title") %>%
  html_text() %>%
  discard(.p = ~stringr::str_detect(.x,"Sale|Bike-Finder|Kinder|E-Bike")) %>%
  enframe(name = "position", value = "category")
# bike_category_char_tbl



# Load Bikes ----

l1 = 1
l2 = nrow(bike_category_char_tbl)
all_bikes <- tibble(position = 1, category = "-" , title = "-" , price = "-" )

for (i in seq(l1, l2)) {

bike_category_url <- bike_category_url_tbl$url[i]
# bike_category_url 
bike_category_char <- bike_category_char_tbl$category[i]
# bike_category_char

# xopen(bike_category_url)


bike_models_title <- read_html(bike_category_url) %>%
  
  html_nodes(css = ".catalog-category-bikes__title-text") %>%
  html_text(trim = TRUE) %>%
  
  enframe(name = "position", value = "title")

# bike_models_title


bike_models_price <- read_html(bike_category_url) %>%
  
  html_nodes(css = ".catalog-category-bikes__price-title") %>%
  html_text(trim = TRUE) %>%
  
  enframe(name = "position", value = "price")

# bike_models_price

L = nrow(bike_models_price)

bike_category <- tibble(position = 1:L, category = c(bike_category_char))
# bike_category

bike_models <- left_join(bike_category, bike_models_title, by = "position") %>%
  left_join(., bike_models_price, by = "position")


print(bike_models)

all_bikes <- all_bikes %>% add_row(bike_models) 

Sys.sleep(10)

}


all_bikes_final <- all_bikes[-c(1), ]
all_bikes_final %>% head(10)


```
